### 2012-07-29 Doc/VRIPHYS2012/vriphys2012.tex
begin of something in section 3.1
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@435 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

We define a local system of coordinates $(x,y,z)$ in which the axis z is oriented along the thickness of the element. (\CD{TODO: figure}) 
For the shell formulation, there is no need to compute the derivatives along axis $z$.

The 2D tensor of deformation can be defined as a $2\times2$ matrix in which the components $k=\{x,y\}$ and $l=\{x,y\}$are:
\begin{equation}
F_{kl} = \frac{\delta T^k}{\delta l}   
\end{equation}

@@

\Figure{\linewidth}{roof}
{Convergence for modified Scordelis-Lo roof test of DKT+ANDES element and
our B\'ezier shell element.}

@@

\Figure{\linewidth}{hemisphere}
{Convergence for test on hemisphere with 18° hole for the DKT+ANDES element and
our B\'ezier shell element.}

>>>>

(\CD{TODO add a figure to illustrate the explanation})

We define a local system of coordinates $(x,y,z)$ in which the axis z is oriented along the thickness of the element\footnote{The computation of the frame of each element will be detailed in section \ref{sec-corot}. }. 
Given the initial position of the triangle points in this system of coordinate, $\{x_1^0, y_1^0\}$,  $\{x_2^0, y_2^0\}$, and  $\{x_3^0, y_3^0\}$, we can compute a linear relation between $\{\xi_1,\xi_2, \xi_3\}$ and $\{ x,y \}$:

\begin{equation}
\left[ \begin{array}[c]{c} \xi_1(x,y) \\ \xi_2(x,y) \\ \xi_3(x,y) \end{array} \right] =
\left[ \begin{array}[c]{ccc}
1 & 1 &  1 \\
x_1^0 & x_2^0 & x_3^0 \\
y_1^0 & y_2^0 & y_3^0
\end{array} \right] ^{-1} 
\left[ \begin{array}[c]{c} 1 \\ x \\ y \end{array} \right] 
\end{equation}

Thus, we can locally compute some spacial derivatives, along $x$ and $y$ on the interpolation function vector $T$ (which has three components $(T^x, T^y, T^z)$ .
The 2D tensor $F$ of the in-plane deformations can be computed as a $2\times2$ matrix where the line $k$ and the column $l$ alternatively represent $x$ and $y$\footnote{It can be noted $k=\{x,y\}$ and $l=\{x,y\}$}:
\begin{equation}
F_{kl} = \frac{\delta T^k}{\delta l}  =  \sum_{j=1}^3 \frac{\delta T^k}{\delta \xi_i} \frac{\delta \xi_i}{\delta l}  
\end{equation}

For the shell formulation, there is no need to compute the derivatives along direction $z$, but the second derivatives derivatives $\frac{\delta T^z}{\delta kl}$...

@@

\Figure{\linewidth}{roof}
{Convergence for modified Scordelis-Lo roof test of DKT+ANDES element and
our B\'ezier shell element. \CD{Can you do the same test with the model used by Comas ?}}

@@

\Figure{\linewidth}{hemisphere}
{Convergence for test on hemisphere with 18° hole for the DKT+ANDES element and
our B\'ezier shell element. \CD{Same question: can you do the same test with the model we used with O.Comas ? Hopefully, it will show that our model has a better convergence ... }}
